Optimal Light Curve Attitude Inversion with Measurement Noise: Two Case Studies

### 2025-03-17 paper.tex
merged plots

\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\usepackage{bm} % for bold math
\usepackage{mathtools} % for \prescript
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{adjustbox}

@@

To demonstrate the effectiveness of our inversion method, we first present results for a simulated light curve where the ground truth is known and material property mismatch is insignificant. We produce a noisy, observed light curve for a high-fidelity model of the Saturn V second stage scaled down by a factor $10/3$ to act as a template rocket body object, shown on the right of Figure \ref{fig:rb_models}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sigma_solsRocket Body.png}
  \caption{Candidate solution initial orientation MRP vectors, ground truth highlighted in red.}
  \label{fig:sigma_sols1}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{omega_sols_Rocket Body.png}
  \caption{Candidate solution initial body-frame angular velocities, ground truth highlighted in red.}
  \label{fig:omega_sols1}
\end{figure}

@@

This light curve shows clear periodicity, but has a high estimated standard deviation and a relatively low sampling rate due to the object's low brightness and the sensor readout time. Inversion was performed using $10^4$ initial guesses with the material and angular velocity assumptions listed in Table \ref{tb:case2_ass}. The candidate solution results are presented in terms of their mean light curves in Figure \ref{fig:case2_s}, inertia ratios in Figure \ref{fig:case2_i}, orientation MRPs in Figure \ref{fig:case2_p}, and angular velocities in Figure \ref{fig:case2_w}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_001_2_00x.png}
  \caption{Candidate solution inertia ratio distribution for the Delta I (Star-37E) rocket body, non-candidate converged minima are plotted in grey.}
  \label{fig:case2_i}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_006.png}
  \caption{Candidate solution orientation MRPs for the Delta I (Star-37E) rocket body, non-candidate converged minima are plotted in grey.}
  \label{fig:case2_p}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_005.png}
  \caption{Candidate solution angular velocities for the Delta I (Star-37E) rocket body, non-candidate converged minima are plotted in grey.}
  \label{fig:case2_w}
\end{figure}

@@

This light curve is sampled more densely than the Delta I observations, and clearly has significantly more intense specular peaks. Inversion was performed using $10^4$ initial guesses with the material and angular velocity assumptions listed in Table \ref{tb:case3_ass}. The candidate solution results are presented in terms of their mean light curves in Figure \ref{fig:case3_s}, inertia ratios in Figure \ref{fig:case3_i}, orientation MRPs in Figure \ref{fig:case3_p}, and angular velocities in Figure \ref{fig:case3_w}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_008.png}
  \caption{Candidate solution orientation MRPs for ECHOSTAR II, non-candidate converged minima are plotted in grey.}
  \label{fig:case3_p}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_007.png}
  \caption{Candidate solution angular velocities for ECHOSTAR II, non-candidate converged minima are plotted in grey.}
  \label{fig:case3_w}
\end{figure}

>>>>

\usepackage{subcaption}
\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\usepackage{bm} % for bold math
\usepackage{mathtools} % for \prescript
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{adjustbox}

@@

To demonstrate the effectiveness of our inversion method, we first present results for a simulated light curve where the ground truth is known. In order to make this simulated case realistic, we use the presented measurement noise models and introduce a mismatch between the ground truth object used to generate the measurements and the model used in inversion. We produce a noisy, observed light curve for a high-fidelity model of the Saturn V second stage scaled down by a factor $10/3$ to act as a template rocket body object, shown on the right of Figure \ref{fig:rb_models}.

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{sigma_solsRocket Body.png}
    \caption{Uniform prior}
    \label{fig:sigma_sols1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{sigma_solsRocket Body Prior.png}
    \caption{Informative prior}
    \label{fig:sigma_sols1b}
  \end{subfigure}

  \caption{Candidate solution initial orientation MRP vectors, ground truth highlighted in red.}
  \label{fig:sigma_sols1}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{omega_sols_Rocket Body.png}
    \caption{Uniform prior}
    \label{fig:omega_sols1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{omega_sols_Rocket Body Prior.png}
    \caption{Informative prior}
    \label{fig:omega_sols1b}
  \end{subfigure}

  \caption{Candidate solution initial body-frame angular velocity vectors, ground truth highlighted in red. TODO: change the perspective on the angular velocities}
  \label{fig:omega_sols1}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{converged_solutions_2_Rocket Body.png}
    \caption{Uniform prior}
    \label{fig:i_sols1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{converged_solutions_2_Rocket Body Prior.png}
    \caption{Informative prior}
    \label{fig:i_sols1b}
  \end{subfigure}

  \caption{Candidate solution inertia ratios, ground truth highlighted in red.}
  \label{fig:i_sols1}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{converged_solutions_3_Rocket Body.png}
    \caption{Uniform prior}
    \label{fig:w_vs_ang_error_sols1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{converged_solutions_3_Rocket Body Prior.png}
    \caption{Informative prior}
    \label{fig:w_vs_ang_error_sols1b}
  \end{subfigure}

  \caption{Candidate solution angular orientation error and angular velocity magnitudes compared to the truth}
  \label{fig:w_vs_ang_error_sols1}
\end{figure}

@@

This light curve shows clear periodicity, but has a high estimated standard deviation and a relatively low sampling rate due to the object's low brightness and the sensor readout time. Inversion was performed using $10^4$ initial guesses with the material and angular velocity assumptions listed in Table \ref{tb:case2_ass}. The candidate solution results are presented in terms of their mean light curves in Figure \ref{fig:case2_s}, orientation MRPs and angular velocities in Figure \ref{fig:case2_pw}, and inertia ratios in Figure \ref{fig:case2_i}.

@@

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=\figmed]{sphx_glr_results_006.png}
%   \caption{}
%   \label{fig:case2_p}
% \end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{sphx_glr_results_006.png}
    \caption{MRP}
    \label{fig:case2_pwa}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{sphx_glr_results_005.png}
    \caption{Angular velocity}
    \label{fig:case2_pwb}
  \end{subfigure}

  \caption{Candidate solution orientation MRPs and angular velocity vectors for the Delta I (Star-37E) rocket body}
  \label{fig:case2_pw}
\end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=\figmed]{sphx_glr_results_005.png}
%   \caption{Candidate solution angular velocities for the Delta I (Star-37E) rocket body}
%   \label{fig:case2_w}
% \end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_001_2_00x.png}
  \caption{Candidate solution inertia ratio distribution for the Delta I (Star-37E) rocket body}
  \label{fig:case2_i}
\end{figure}

@@

This light curve is sampled more densely than the Delta I observations, and clearly has significantly more intense specular peaks. Inversion was performed using $10^4$ initial guesses with the material and angular velocity assumptions listed in Table \ref{tb:case3_ass}. The candidate solution results are presented in terms of their mean light curves in Figure \ref{fig:case3_s}, orientation MRPs and angular velocities in Figure \ref{fig:case3_pw}, and inertia ratios in Figure \ref{fig:case3_i}.

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{sphx_glr_results_008.png}
    \caption{MRP}
    \label{fig:case3_pwa}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.23\textwidth}
    \centering
    \includegraphics[width=\textwidth]{sphx_glr_results_007.png}
    \caption{Angular velocity}
    \label{fig:case3_pwb}
  \end{subfigure}

  \caption{Candidate solution orientation MRPs and angular velocity vectors for ECHOSTAR II}
  \label{fig:case3_pw}
\end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=\figmed]{sphx_glr_results_008.png}
%   \caption{Candidate solution orientation MRPs for ECHOSTAR II, non-candidate converged minima are plotted in grey.}
%   \label{fig:case3_p}
% \end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=\figmed]{sphx_glr_results_007.png}
%   \caption{Candidate solution angular velocities for ECHOSTAR II, non-candidate converged minima are plotted in grey.}
%   \label{fig:case3_w}
% \end{figure}
